---
title: "Diamond Report Example"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

`r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")` 
`r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")`
`r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")`
`r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")`
`r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")`
`r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")` `r emo::ji("gem")`


# {.tabset}



```{r libraries, echo=FALSE}
library(tidyverse)    # take all that is good about this universe
library(knitr)        # knit your rmarkdown
library(kableExtra)   # make better tables
library(ggridges)     # make ridgeline plots
library(dotwhisker)   # make dwplot easily for regression vis
library(here)         # never rely on local paths again
library(janitor)      # clean things up easily!
library(emo)          # use emojis in rmarkdown :-)
library(scales)       # add scale elements to x and y axes

options(scipen = 999)
```


```{r}
data("diamonds")
```


## Cut, Color, and Carat 


<div class="panel panel-default">
<div class="panel-heading"> <h2>Cut</h2> </div>
<div class="panel-body">

```{r}
diamonds %>% 
  group_by(cut) %>% 
  summarise(Min = round(min(price), 0),
            Q1 = round(quantile(price, 1/4), 0),
            Median = round(median(price), 0),
            Mean = round(mean(price), 0),  
            Q3 = round(quantile(price, 3/4), 0),
            Max = round(max(price), 0)) %>% 
  kable(format = "markdown", format.args = list(big.mark = ','), 
        col.names = c("Group", "Min", "Q1", "Median", "Mean", "Q3", "Max")) %>%
  kable_styling(full_width = F, position = "left")

```

It looks as though cut is not the only variable that influences price 

</div>
</div>


<div class="panel panel-default">
<div class="panel-heading"> <h2>Color</h2> </div>
<div class="panel-body">

```{r}
diamonds %>% 
  group_by(color) %>% 
  summarise(Min = round(min(price), 0),
            Q1 = round(quantile(price, 1/4), 0),
            Median = round(median(price), 0),
            Mean = round(mean(price), 0),  
            Q3 = round(quantile(price, 3/4), 0),
            Max = round(max(price), 0)) %>% 
  kable(format = "markdown", format.args = list(big.mark = ','), 
        col.names = c("Group", "Min", "Q1", "Median", "Mean", "Q3", "Max")) %>%
  kable_styling(full_width = F, position = "left")

```


It looks as though color D is the cheapest and 
median and mean price both seem to generally 
go to up at each letter to color J 

</div>
</div>


<div class="panel panel-default">
<div class="panel-heading"> <h2>Relationship Between Carat and Price</h2> </div>
<div class="panel-body">

```{r}
diamonds %>% 
  ggplot(aes(carat, price)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Carat", y = "Price")
```

</div>
</div>


<div class="panel panel-default">
<div class="panel-heading"> <h2>Relationship Between Carat, Cut, Color, and Price </h2> </div>
<div class="panel-body">
```{r}
diamonds %>% 
  ggplot(aes(carat, price, color = color)) +
  geom_point() +
  facet_wrap(~cut) + 
  theme_minimal() +
  labs(x = "Carat", y = "Price")
```

</div>
</div>

## Model 

```{r}
d1 <- 
  diamonds %>% 
  mutate(color = factor(color, ordered = FALSE), 
         cut = factor(cut, ordered = FALSE))

reg1 <- lm(price ~ carat + color + cut, d1)
options(digits = 2)
# summary(reg1)
```


<div class="panel panel-default">
<div class="panel-heading"> <h2>Regression Coefficients </h2> </div>
<div class="panel-body">
```{r}
reg1 <- broom::tidy(reg1)

dotwhisker::dwplot(reg1) +
  theme_minimal() +
  theme(legend.position = "none") +
  geom_vline(xintercept = 0, colour = "grey60", linetype = 3) +
  scale_x_continuous(labels = dollar)
```

</div>
</div>